\chapter{Bibliograf\'ia}
\label{sec:biblio}
[1] BAKSHI, Kapil. Considerations for Big Data: Architecture and Approach. En: Aerospace Conference IEEE. Memorias.  Big Sky, MT. 2012.
\paragraph{}
[2] CUZZOCREA, Alfredo. Analytics over Large-Scale Multidimensional Data: The Big Data Revolution!. En: Conference on Information and Knowledge Management. Memorias. ACM  New York, NY, USA 2011. p. 101-104.
\paragraph{}
[3] Proceedings of the VLDB Endowment Volume 5 [Online]. Istanbul:  LABRINIDIS, Alexandros. Challenges and opportunities with big data August 2012. Disponible en internet: \textless http://dl.acm.org/citation.cfm?id=2367572\textgreater
\paragraph{}
[4] CHAUDHURI, Surajit, What Next? A Half-Dozen Data Management Research Goals for Big Data and the Cloud. En: International Conference on Management of Data. Memorias. ACM New York, NY, USA 2012. p. 1-4.
\paragraph{}
[5] GOPALKRISHNAN, Vivekanand, Big Data, Big Business: Bridging the Gap. En: Knowledge Discovery and Data Mining. Memorias. ACM New York, NY, USA 2012. p. 7-11.
\paragraph{}
[6] BORKAR Vinayak, Inside “Big Data Management”: Ogres, Onions, or Parfaits?. En: Extending Database Technology. Memorias. ACM New York, NY, USA 2012. p. 3-14.
\paragraph{}
[7] ZIKOPOULOS, Paul et al. Understanding Big Data: Analytics for Enterprise Class Hadoop and Streaming Data. McGraw-Hill. 2012.
\paragraph{}
[8] USENIX Association Berkeley [Online]. CA, USA:  Dean Jeffrey y  Ghemawat Sanjay. MapReduce: simplified data processing on large clusters. 2004 Disponible en internet \textless http://dl.acm.org/citation.cfm?id=1251264\textgreater
\paragraph{}
[9]  MANYIKA, James et al.  Big Data: The next frontier for innovation, competition and productivity. Mckinsey Global Institute. May 2011.
\paragraph{}
[10] SAS Institute.  Big Data: Harnessing a game-changing asset. Reporte de Economist Intelligence Unit. Septiembre 2011.
\paragraph{}
[11] YEUNG, Ken. Now counting 6.2 million daily, Foursquare has crossed the 3 billion check-in mark. The Next Web [Online]. 21 noviembre 2012 [Citado 27 noviembre 2012].Disponible en internet \textless http://thenextweb.com/location/2012/11/21/foursquare-has-its-3-billionth-check-in-seeing-growth-of-x/\textgreater
\paragraph{}
[12] Foursquare. About foursquare[Online]. Disponible en internet 
\textless https:// foursquare.com/about/\textgreater
\paragraph{}
[13] Harvard Bussines Review. Hbr Insigth Center[Online]. Harvard Bussines Review Octubre - Noviembre 2012 [citado 27 Noviembre 2012]. Disponible en internet 
\textless http://hbr.org/special-collections/insight/big-data\textgreater
\paragraph{}
[14] Foursquare. Foursquare connects people to businesses[Online]. Disponible en internet 
\textless http:// foursquare.com/business\textgreater
\paragraph{}
[15]Foursquare. Advertise with Foursquare[Online]. Disponible en internet 
\textless http:// business.foursquare.com/advertise/\textgreater
\paragraph{}
[16] Hoot Suite. Gestion de redes sociales[Online]. Disponible en internet 
\textless http:// hootsuite.com/features/social-networks\textgreater
\paragraph{}
[17]SCHIFFMAN , Leon G. KANUK , Leslie L. El comportamiento del consumidor. Pearson Educaci\'on (Agosto 2005).
\paragraph{}
[18]KOTLER, Philip.  Fundamentos de Marketing (6ª edici\'on). Pearson Educaci\'on de M\'exico. 2003
\paragraph{}
[19]King, Kevin F., Geolocation and Federalism on the Internet: Cutting Internet Gambling’s Gordian Knot (July 14, 2009). Columbia Science and Technology Law Review, Vol. XI, 2010.
\pagebreak